Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-19 doc/JFLA2022/paper.tex
qualify the bridge code more
paragraph on portability of Alectryon snippet generation

The initial bridge code uses the SSReflect proof language and idioms from the Mathematical Components library. We made this design decision since we believe it is less challenging to reason about Hydra-battles code using SSReflect and MathComp than to reason about Gaia without SSReflect.

@@

@@

\paragraph{The Docker-Coq-Action~\cite{martindorel2020dockercoq}.}
This GitHub Action provides a very simple way of setting up Continuous Integration (CI) for a Coq project with an opam file.
%
At the current time, we rely on it, together with the mathcomp Docker images~\cite{mathcompdocker}, to test our two main libraries, Hydra-battles and Addition-chains, with multiple versions of Coq.

>>>>

The initial draft bridge code mostly uses the SSReflect proof language and idioms from the Mathematical Components library. We made this design decision since we believe it is less challenging to reason about Hydra-battles code using SSReflect and MathComp than to reason about Gaia without SSReflect.

@@

\paragraph{Applications in other proof assistants.}
The Alectryon toolchain is intended to eventually support the languages of many proof assistants, and already has preliminary support for Lean~3. Our Alectryon extensions for snippet generation are in principle applicable to any language supported by Alectryon. However, snippet delimiters are language specific, and our tooling currently assumes Coq-compatible delimiters; we expect to lift this restriction in the near future. We view \Hydras as an incubator for experimental Alectryon features that, when deemed stable and useful, can be disseminated to a wider audience including users of other proof assistants.

@@

\paragraph{Docker-Coq-Action~\cite{martindorel2020dockercoq}.}
This GitHub Action provides a very simple way of setting up Continuous Integration (CI) for a Coq project with an opam file.
%
At the current time, we rely on it, together with the mathcomp Docker images~\cite{mathcompdocker}, to test our two main libraries, Hydra-battles and Addition-chains, with multiple versions of Coq.
